Data_Import

### 2023-04-17 Anxiety_Vis.Rmd
Made sociodem figs, and changed titles for anxiety figs

#### Race
```{r}
#Overall race
Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(0,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
   geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

@@

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
EducationDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Education Level",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Education Level",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    title ="Education Level",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Education Level",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

@@

Break it up by duration group (Year)
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
YEARTXDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
YEARTXDF1<-YEARTXDF1[1:40,]
# plot
YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
    labs(title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

>>>>

#### Race
```{r}
#Overall race
Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
   geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

@@

Break it up by duration group 
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
EducationDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
EducationDF1<-EducationDF1[1:45,]
# plot
Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Education Level",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

@@

Break it up by duration group (Year)
```{r, include= FALSE}
#Create a New Data Set with an Average Anxiety Variable and Gender
YEARTXDF1<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
YEARTXDF1<-YEARTXDF1[1:40,]
# plot
YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 1-5 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
    labs(
      # title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 6-10 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="Anxiety Severity by YEARTX",
    subtitle = "Patient discharge 11-15 days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

@@

# plot
YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=.5)+
  geom_point(size=.5)+
  labs(
    # title ="",
    subtitle = "Patient discharge 16+ days")+
    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

### 2023-04-17 Data_Import.Rmd
Made sociodem figs, and changed titles for anxiety figs

                    Referal_1 = as.factor(Referal_1),
                    Referal_1 = recode(Referal_1,

@@

ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))
```

@@

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  coord_polar("y",start=0)+
  theme_void()
```

>>>>

@@

ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))

### Bar chart for race ###
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Bar chart for gender###
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Year ###

Mothership$TxYear

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

@@

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  coord_polar("y",start=0)+
  theme_void()
```
